---
title: "vharipur_qmm2"
author: "Vaishnavi"
date: "2023-09-24"
output: html_document
---
---
title: "QMM assignment 2"
author: "Vaishnavi"
date: "2023-09-24"
output: html_document
---

#DECISION VARIABLES

Let A1, B1, and C1 be large, medium, and small sizes of product in Plant-1
Let A2, B2, and C2 be large, medium, and small sizes of product in Plant-2
Let A3, B3, and C3 be large, medium, and small sizes of product in Plant-3

#LINEAR PROGRAMMING MODEL

#Decision variables

Ax, Bx, Cx

#Objective Function

Max Z=420A1+420A2+420A3+360B1+360B2+360B3+300C1+300C2+300C3

Constraints

1.	Based on excess capacity in plants 1,2, and 3
             A1+B1+C1 <= 750 
             A2+B2+C2 <= 900 
             A3+B3+C3 <= 450

2.	Based on Storage Capacity in Plants1,2, and 3 respectively
              20A1+15B1+12C1 <= 13000 
              20A2+15B2+12C2 <= 12000 
              20A3+15B3+12C3 <= 5000

3.	Based on Sales forecast/ Demand for Large, Medium, and Small sized products
              A1+A2+A3 <= 900 
              B1+B2+B3 <= 1200 
              C1+C2+C3 <= 750

#Also-> Ax, Bx, Cx >= 0, non-negative quantity

#Given that each plant should use equal percentage of its excess capacity production.

900(A1+B1+C1) = 750(A2+B2+C3) 450(A1+B2+C2) = 900(A3+B3+C3)

#Subject to- A1,A2,A3,B1,B2,B3,C1,C2,C3 >=0 ……Non-negativity quantities

The above LP problem constaraints can be written as

A1 + B1 + C1 + 0A2 + 0B2 + 0C2 + 0A3 + 0B3 + 0C3 ≤ 750
0A1 + 0B1 + 0C1 + A2 + B2 + C2 + 0A3 + 0B3 + 0C3 ≤ 900
0A1 + 0B1 + 0C1 + 0A2 + 0B2 + 0C2 + A3 + B3 + C3 ≤ 450
20A1 + 15B1 + 12C1 + 0A2 + 0B2 + 0C2 + 0A3 + 0B3 + 0C3 ≤ 13000
0A1 + 0B1 + 0C1 + 20A2 + 15B2 + 12C2 + 0A3 + 0B3 + 0C3 ≤ 12000
0A1 + 0B1 + 0C1 + 0A2 + 0B2 + 0C2 + 20A3 + 15B3 + 12C3 ≤ 5000
A1 + 0B1 + 0C1 + A2 + 0B2 + 0C2 + A3 + 0B3 + 0C3 ≤ 900
0A1 + B1 + 0C1 + 0A2 + B2 + 0C2 + 0A3 + B3 + 0C3 ≤ 1200
0A1 + 0B1 + C1 + 0A2 + 0B2 + C2 + 0A3 + 0B3 + C3 ≤ 750


```{r}
library(lpSolve)

Objective <- c(420,420,420,360,360,360,300,300,300)
Objective
```

```{r} 
constraints <- matrix(c(1,1,1,0,0,0,0,0,0,
0,0,0,1,1,1,0,0,0,
0,0,0,0,0,0,1,1,1,
20,15,12,0,0,0,0,0,0,
0,0,0,20,15,12,0,0,0,
0,0,0,0,0,0,20,15,12,
1,0,0,1,0,0,1,0,0,
0,1,0,0,1,0,0,1,0,
0,0,1,0,0,1,0,0,1,
900,900,900,-750,-750,-750,0,0,0,
0,0,0,450,450,450,-900,-900,-900,
450,450,450,0,0,0,-750,-750,-750),nrow = 12,byrow = TRUE)
constraints
```

```{r}
#we can set the direction of the inequalities using subject to equation for this by using directions function
directions <- c("<=",
"<=",
"<=",
"<=",
"<=",
"<=",
"<=",
"<=",
"<=",
"=",
"=",
"=")
directions

```


```{r}
#setting RHS 
RHS <- c(750,
900,
450,
13000,
12000,
5000,
900,
1200,
750,
0,
0,
0)
RHS
```

```{r}
#to get objective function value
maximum <- lp("max",Objective,constraints,directions,RHS)
maximum
```

```{r}
#to get values of each variable
lp("max", Objective,constraints,directions,RHS)$solution
```

